There are no small Advantages: Reinforcement learning in near continuous time with Deep RelAtive Mixture of Advantages

### 2019-01-14 paper/icml_drau/framework.tex

%! TEX root = icml_drau.tex
\section{Near continuous time reinforcement learning}
\label{sec:framework}
% In this section, a continuous reinforcement learning framework is introduced,
% and it is shown that under this framework, the state-action value function does
% not depend on the action. We further show that in near continous domains, when
% the discretization timestep $\deltat$ is small, the difference in state-action
% value between two different actions in a fixed state is of order $\bigO(\deltat)$.

Many reinforcement learning environments are discretizations or approximations
of continuous environments. We say that these environments are \emph{near
continuous}. This includes usual control environment (Mujoco, Gym, ...)
\TODO{Cite}. In practice, these environments are considered as discrete, and a
time discretization $\deltat$ is fixed by the simulator. In real environments,
like in robotics, the time discretization $\deltat$ is fixed by the sensors or
motors. Still, in these environments, there is an uderlying continuous process
which do not depend on $\deltat$. Therefore, our learning methods should be
invariant to $\deltat$, as well as all the meaningfull quantities we are using.

In this paper, we try to analyze \emph{near-continuous} environments when  modifying $\deltat$, especially when $\deltat \rightarrow 0$. In order to design algorithms more robust to the choice of $\deltat$, we want that when $\deltat \rightarrow 0$, the quantities we are using and our algorithm do converge to meaningful limit quantities and algorithms.

\TODO{We should explain that, if not invariant, harder to find good hyperparameters}

In this section, we first introduce our framework. Then we show how we can define the return, discount factor and Value function such that it has a limit when $\deltat \rightarrow 0$. Finally, we show that there is no Action-Value function in continuous MDPs.

\VC{Many reinforcement learning environments are not intrinsically time
	discrete, but discretization of an underlying continuous time
	environment. For instance, many control environments, such as the
	Mujoco~\cite{ddpg} environments or OpenAI Gym classic~!CITE! control
	environments are discretization of continuous time control problems.
	For real world environments, the discretization timestep, $\deltat$ is
	most often imposed by the quality of sensors and actuators. For visual
	simulated environments, it often corresponds to the number of frames
	that the simulator generates per second. As $\deltat$ is not an
	intrinsic parameter of the environment, but a constraint imposed by
	computational ressources, we would expect that decreasing $\deltat$
	could  only improve the performance of reinforcement learning agents.
	To achieve this goal, reinforcement learning algorithms should be
	resilient to a change of $\deltat$, and should remain viable when
	$\deltat \rightarrow 0$. We are thus interested in the behavior of
	reinforcement learning algorithms in discretized environments, when the
	discretization timestep is small. We will refer to such environments as
	\emph{near continuous environments}.

	In what follows, a formalized view of near continuous environments is given,
	along with $\deltat$ dependant definitions of return, discount factor and
	value functions. With these definitions, each of these quantities is shown
	to converge to a well defined continous time limit. Finally, it is shown
	that the state-action value function collapses to the value function as
	$\deltat$ goes to $0$, and consequently that there is no Q-learning in
	continuous time.
}
\subsection{Framework}

We say that ${\cal M}_\deltat = \langle {\cal S}, {\cal A}, T_{\deltat},
r_\deltat, \gamma_\deltat\rangle$ is a \emph{near-continuous} Markov Decision
Process with trajectories $(s_\deltat^k)_{k\in\mathbb{N}}$ if there is a
\emph{physical time} $\deltat$ between two observations, and if
$s_\deltat^{k+1}$ is close to $s_\deltat^k$. We assume that the state space
${\cal S}$ is continuous \TODO{True? Ok?}. The action space ${\cal A}$ can be
either continuous or discrete \TODO{except in the theorems}.

% Many practical Reinforcement Learning are near-continuous: For example, in a simulated physical environment in which the $\deltat$ is fixed by the simulator, or in a real environments, if the agent is a robot.

% , the $\deltat$ is fixed by the sensitivity of the sensors and the reactivity of the motors. We assume that the state space ${\cal S}$ is continuous.

If the \emph{near continuous} MDP is the discretization, or a good approximation, of continuous MDP, Iwe can assume that the agent is actually is following a diffusion process:
\begin{equation}
  \label{eq:diffusion}
  ds = F(s, a)dt + \Sigma(s, a)\dbt
\end{equation}
where $F: {\cal S}\times{\cal A}\rightarrow {\cal S}$ describes the physics of the environment, and $\dbt$ is the noise of the environment. In that case, the transition function is: $T_\deltat(s, a, s')$ is a probability distribution over $s'$, which is the distribution of $s_\deltat$ if $(s_t)_{t\in\mathbb{R_+}}$ is following equation (\ref{eq:diffusion}), $s_0 = s$ and the action is $a$ during the interval $[0, \deltat]$. If the environment is deterministic as in classical control theory, or in many usual simulated environments (Mujoco, Gym, ...), we have $\Sigma = 0$.

In this work we only consider deterministic policies $\pi: {\cal S} \rightarrow {\cal A}$. Therefore, the diffusion equation becomes:
\begin{equation}
  \label{eq:diffusion-policy}
  ds = F(s, \pi(s))dt + \Sigma(s, \pi(s))\dbt
\end{equation}

\TODO{Les deux paragraphes suivants sont redondants avec l'intro de la section}
If we assume that the \emph{near continuous} MDP we are observing is a discretization of a continuous MDP \TODO{for example which could follow a diffusion process as in Equation (\ref{eq:diffusion})}, then we know that the time discretization $\deltat$ is not intrisically related to the problem we are tackling. Therefore, our algorithm should be robust to different choices of $\deltat$. For example, in a simulated environment where the $\deltat$ only depends on the FPS, or in a real environment in which the $\deltat$ is defined by the reactivity of the sensors and motors, we would like our algorithms to be robust if the FPS in changed, or if we use more reactive sensors.

In this paper, we try to design RL methods for \emph{near continuous} MDP robust to the choice of $\deltat$. Our method is to analyse the different quantities we are looking at when $\deltat$ is changing, and especially when $\deltat \rightarrow 0$, and make sure that the quantities we are interested in and our algorithms do converge to meaningful limit quantities and algorithms. \TODO{OK?} The first formal statement we can make on discretized MDP with a time discretization $\deltat$ is that if $\deltat \rightarrow 0$, the distribution of trajectories do converge to the continuous trajectories.

\begin{theorem}
  Assume that $\pi: {\cal S} \rightarrow {\cal A}$ is a continuous and deterministic policy. Let $(s_t)_{t\in\mathbb{R}_+}$ be the continuous process by following \eqref{eq:diffusion} and $(s_\deltat^k)$ be the discrete process obtained if the agent only get observations every $\deltat$ \TODO{explain better}.

  We define the time process $\tilde s_\deltat^t = s^{\lfloor \frac{t}{\deltat}\rfloor}_\deltat$ for $t\in\mathbb{R_+}$.\TODO{Explain}. Then:
  \begin{equation}
    \label{eq:conv-traj}
    (\tilde s_\deltat^t)_{t\in\mathbb{R}_+} \rightarrow_{\deltat \rightarrow 0} (s_t)_{t\in\mathbb{R}_+}
  \end{equation}
  as probability distributions.
\end{theorem}

\VC{Consider ${\cal S} = \mathbb{R}^d$ a set of states, and ${\cal A}$ a set of
	actions. A familly of \emph{Markov decision processes} ${\cal
	M}_\deltat = \langle {\cal S}, {\cal A}, T_{\deltat}, r_\deltat,
	\gamma_\deltat\rangle$ is \emph{near continous} if for any
	deterministic policy $\pi:{\cal S} \rightarrow {\cal A}$, trajectories
	of ${\cal M}_\deltat$ converge to stochastic processes that satisfy the
	Stochastic differential equation
	\begin{equation}
		\label{eq:diffusion}
		ds = F(s, a)dt + \Sigma(s, a)\dbt.
	\end{equation}
	Informally $F: {\cal S}\times{\cal A}\rightarrow {\cal S}$ describes
	the deterministic dynamic of the environment, while $\Sigma(s, a)\dbt$
	describes its stochasticity. Notably, $\Sigma = 0$ if the environment is
	deterministic, as in classical control theory, or in many usual simulated
	environments (Mujoco, Gym, ...).

@@

	In this paper, we try to design RL methods for \emph{near continuous} MDP
	robust to the choice of $\deltat$. Our method is to analyse the different
	quantities we are looking at when $\deltat$ is changing, and especially when
	$\deltat \rightarrow 0$, and make sure that the quantities we are interested in
	and our algorithms do converge to meaningful limit quantities and algorithms.
	!OK?! The first formal statement we can make on discretized MDP with a
	time discretization $\deltat$ is that if $\deltat \rightarrow 0$, the
	distribution of trajectories do converge to the continuous trajectories.

@@

		We define the time process $\tilde s_\deltat^t = s^{\lfloor
		\frac{t}{\deltat}\rfloor}_\deltat$ for
		$t\in\mathbb{R_+}$.!Explain!. Then:
		\begin{equation}
			\label{eq:conv-traj}
			(\tilde s_\deltat^t)_{t\in\mathbb{R}_+} 
			\xrightarrow[\deltat \rightarrow 0]{} (s_t)_{t\in\mathbb{R}_+}
		\end{equation}
		in distribution.
	\end{theorem}
}

@@

	On the contrary, the definition of $\gamma_\deltat$ in
	Eq.~\eqref{eq:def-gamma} yields an approximately constant macroscopic
	time horizon when $\deltat$ goes to $0$. Indeed,
	\begin{equation}
		\label{eq:time-horizon}
		\frac{\deltat}{1-\gamma^\deltat}
		= - \frac{1}{\log \gamma} + \bigO(\deltat)
		\approx \frac{1}{1-\gamma}
	\end{equation}
}
The definition of $\gamma_\deltat$ in equation (\ref{eq:def-gamma}) is consistent with what we expect for the time horizon. We know \TODO{Cite?} that for a MDP with discount factor $\gamma$, the time horizon is $\frac{1}{1-\gamma}$ steps. But if the duration of a step is $\deltat$, the time horizon in \emph{physical time} is $\frac{\deltat}{1-\gamma}$, which goes to 0 if $\deltat \rightarrow 0$.
% This means that if $\gamma$ is not adapted to $\deltat$, the return $R_\deltat(\tau) = \sum_{k=0}^\infty\gamma^{k}r(s^\deltat_k, a^\deltat_k)\deltat \rightarrow_{\deltat\rightarrow 0} r(s_0, a_0)$. \TODO{A changer pour ne pas ecrire de chose fausse}
But in practice, for example on a control problem, we do not care about the time horizon as a number of steps but as a \emph{physical} quantity independant of $\deltat$. With $\gamma_\deltat = \gamma^\deltat$, the time horizon in \emph{physical time} is:
\begin{equation}
  \label{eq:time-horizon}
  \frac{\deltat}{1-\gamma^\deltat} \rightarrow_{\deltat \rightarrow 0} - \frac{1}{\log \gamma} \approx \frac{1}{1-\gamma}
\end{equation}

@@

The definition of the return Eq.~\eqref{eq:continuous-return}, yields the
following definition of the continuous value function
\begin{equation}
  V^\pi(s) = \E_{\tau\sim\pi}\left[\int\limits_{0}^\infty \gamma^{t}\deltat r_{t} \mid s_0 = s\right].
\end{equation}
The corresponding discretization for time discretization $\deltat$ is
\begin{equation}
  V^\pi_\deltat(s) = \E_{\tau\sim\pi}\left[\sum\limits_{k=0}^\infty \gamma^{k\deltat}\deltat r_{k\deltat} \mid s_0 = s\right]
\end{equation}
which fits the usual definition of the discrete V-function for $\gamma_\deltat$ and
$r_\deltat$ defined in~(\ref{eq:def-gamma}, \ref{eq:def-reward}).
We have the following convergence theorem of the discretized value function to the continuous value function:
  \begin{theorem}
    We have, for all $s \in {\cal S}$:
    \begin{equation}
      \label{eq:conv-value}
      \lim_{\deltat \rightarrow 0} V^\pi_\deltat(s) = V^\pi(s)
    \end{equation}
  \end{theorem}

>>>>

%! TEX root = icml_drau.tex
\section{Near continuous time reinforcement learning}
\label{sec:framework}

  Many reinforcement learning environments are not intrinsically time
	discrete, but discretization of an underlying continuous time
	environment. For instance, many control environments, such as the
	Mujoco~\cite{ddpg} environments or OpenAI Gym classic~!CITE! control
	environments are discretization of continuous time control problems,
        \LB{with a discretization timestep $\deltat$ fixed by the simulator}.
	For real world environments, the discretization timestep, $\deltat$ is
	most often imposed by the quality of sensors and actuators. For visual
	simulated environments, it often corresponds to the number of frames
	that the simulator generates per second. As $\deltat$ is not an
	intrinsic parameter of the environment, but a constraint imposed by
	computational ressources, we would expect that decreasing $\deltat$
	could  only improve the performance of reinforcement learning agents.
	To achieve this goal, reinforcement learning algorithms should be
	resilient to a change of $\deltat$, and should remain viable when
	$\deltat \rightarrow 0$. We are thus interested in the behavior of
	reinforcement learning algorithms in discretized environments, when the
	discretization timestep is small. We will refer to such environments as
	\emph{near continuous environments}.

	In what follows, a formalized view of near continuous environments is given,
	along with $\deltat$ dependant definitions of return, discount factor and
	value functions. With these definitions, each of these quantities is shown
	to converge to a well defined continous time limit. Finally, it is shown
	that the state-action value function collapses to the value function as
	$\deltat$ goes to $0$, and consequently that there is no Q-learning in
	continuous time.
      \TODO{We should explain somwhere here that, if not invariant, harder to find good hyperparameters}
\subsection{Framework}

\VC{
  Consider ${\cal S} = \mathbb{R}^d$ a set of states, and ${\cal A}$ a set of
	actions. A familly of \emph{Markov decision processes} ${\cal
	M}_\deltat = \langle {\cal S}, {\cal A}, T_{\deltat}, r_\deltat,
	\gamma_\deltat\rangle$ is \emph{near continous} if for any
	deterministic policy $\pi:{\cal S} \rightarrow {\cal A}$, trajectories
	of ${\cal M}_\deltat$ converge to stochastic processes that satisfy the
	Stochastic differential equation
	\begin{equation}
		\label{eq:diffusion}
		ds = F(s, a)dt + \Sigma(s, a)\dbt.
	\end{equation}
	Informally $F: {\cal S}\times{\cal A}\rightarrow {\cal S}$ describes
	the deterministic dynamic of the environment, while $\Sigma(s, a)\dbt$
	describes its stochasticity. Notably, $\Sigma = 0$ if the environment is
	deterministic, as in classical control theory, or in many usual simulated
	environments (Mujoco, Gym, ...).

@@

      }

      \LB{
        [[What I don't like in that version is that it is too formal ...]]
        Consider ${\cal S} = \mathbb{R}^d$ a set of states, and ${\cal A}$ a set of
	actions. Assume that an agent is following the continuous Markov Decision Process defined by the Stochastic Differential Equation:
        \begin{equation}
		\label{eq:diffusion}
		ds = F(s, a)dt + \Sigma(s, a)\dbt.
              \end{equation}
        Then, for any $\deltat$, we say that the discrete \emph{Markov decision processes} ${\cal
	M}_\deltat = \langle {\cal S}, {\cal A}, T_{\deltat}, r_\deltat,
      \gamma_\deltat\rangle$ is a discretization of the continuous MDP with \emph{time discretization} $\deltat$ if the transition probability $T_\deltat(s, a, s')$ is the probability distribution of $s_\deltat$, with $s_0 = s$ and the action is $a_t=a$ during the interval $[0, \deltat]$. We say the the MDP ${\cal M}_\deltat$ is \emph{near-continuous}. [[Pb here: we require an uderlying continuous process: there is no intrinsic near continuous process]]

      Informally $F: {\cal S}\times{\cal A}\rightarrow {\cal S}$ describes
	the deterministic dynamic of the environment, while $\Sigma(s, a)\dbt$
	describes its stochasticity. Notably, $\Sigma = 0$ if the environment is
	deterministic, as in classical control theory, or in many usual simulated
	environments (Mujoco, Gym, ...).
      }

        In this paper, we try to design RL methods for \emph{near continuous} MDP
	robust to the choice of $\deltat$. Our method is to analyse the different
	quantities we are looking at when $\deltat$ is changing, and especially when
	$\deltat \rightarrow 0$, and make sure that the quantities we are interested in
	and our algorithms do converge to meaningful limit quantities and algorithms.\TODO{Better formulation maybe?}

        \LB{In that direction, the first thing to do is to check that the discretized
          trajectory do converge to the continuous ones. This is stated in the following theorem. [[Tres tres mal dit, mais c'est l'idee]]
        }
        % The first formal statement we can make on discretized MDP with a
	% time discretization $\deltat$ is that if $\deltat \rightarrow 0$, the
	% distribution of trajectories do converge to the continuous trajectories.

@@

		We define the time process $\tilde s_\deltat^t = s^{\lfloor
		\frac{t}{\deltat}\rfloor}_\deltat$ for
		$t\in\mathbb{R_+}$.!Explain!. Then:
		\begin{equation}
			\label{eq:conv-traj}
			(\tilde s_\deltat^t)_{t\in\mathbb{R}_+} 
			\xrightarrow[\deltat \rightarrow 0]{} (s_t)_{t\in\mathbb{R}_+}
		\end{equation}
		in distribution.
	\end{theorem}

@@

	On the contrary, the definition of $\gamma_\deltat$ in
	Eq.~\eqref{eq:def-gamma} yields an approximately constant macroscopic
	time horizon when $\deltat$ goes to $0$. Indeed,
	\begin{equation}
		\label{eq:time-horizon}
		\frac{\deltat}{1-\gamma^\deltat}
		= - \frac{1}{\log \gamma} + \bigO(\deltat)
		\approx \frac{1}{1-\gamma}
	\end{equation}
      }

      \LB{ \paragraph{Number of steps / Physical time: Time horizon}
        % [[I prefer to talk about ``number of steps'' VS ``Physical time'' than microscopic/Macroscopic]]
        In near continuous environments, there are two notions of time,
	the number of steps, or the number of actions taken, and the actual amount of time spent
	in the underlying continuous time environment, which we call the physical
	time. If $t$ is the real time and $k$ the number of steps, the two are related through $t = k \deltat$.

	The notion of time horizon, which is, informally, the amount of time on
	which the agent optimizes its return, is only meaningful in physical
	time.

        %Having a time horizon of $10$ steps means something very different
	%if $\deltat = 0.1$ and if $\deltat = 0.0001$.

        A rule of thumb
	is that the time horizon of an agent with discount factor $\gamma$ is
	of order $\frac{1}{1 - \gamma}$. If $\gamma_\deltat$ was left constant
	as $\deltat$ goes to $0$, the corresponding macroscopic time horizon 
	would write as $\frac{\deltat}{1 - \gamma}$ which goes to $0$ when
	$\deltat$ goes to $0$.

	On the contrary, the definition of $\gamma_\deltat$ in
	Eq.~\eqref{eq:def-gamma} yields an approximately constant macroscopic
	time horizon when $\deltat$ goes to $0$. Indeed,
	\begin{equation}
          \label{eq:time-horizon}
          \frac{\deltat}{1-\gamma^\deltat}
          = - \frac{1}{\log \gamma} + \bigO(\deltat)
          \approx \frac{1}{1-\gamma}
        \end{equation}

      }

@@

\LB{I did not change this part}
The definition of the return Eq.~\eqref{eq:continuous-return}, yields the
following definition of the continuous value function
\begin{equation}
  V^\pi(s) = \E_{\tau\sim\pi}\left[\int\limits_{0}^\infty \gamma^{t}\deltat r_{t} \mid s_0 = s\right].
\end{equation}
The corresponding discretization for time discretization $\deltat$ is
\begin{equation}
  V^\pi_\deltat(s) = \E_{\tau\sim\pi}\left[\sum\limits_{k=0}^\infty \gamma^{k\deltat}\deltat r_{k\deltat} \mid s_0 = s\right]
\end{equation}
which fits the usual definition of the discrete V-function for $\gamma_\deltat$ and
$r_\deltat$ defined in~(\ref{eq:def-gamma}, \ref{eq:def-reward}).
We have the following convergence theorem of the discretized value function to the continuous value function:
  \begin{theorem}
    We have, for all $s \in {\cal S}$:
    \begin{equation}
      \label{eq:conv-value}
      \lim_{\deltat \rightarrow 0} V^\pi_\deltat(s) = V^\pi(s)
    \end{equation}
  \end{theorem}

### 2019-01-14 paper/icml_drau/icml_drau.tex
Advances.
very first version of the framework part, lots of thing missing but the main structure is there
First figure

% Recommended, but optional, packages for figures and better typesetting:
\usepackage{amsmath, amssymb}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{booktabs} % for professional tables
\usepackage{xcolor}
\usepackage{algorithmic}

@@

@@

\begin{abstract}
	Despite remarkable successes, \emph{Deep Reinforcement learning} remains sensitive to
	hyperparameterization, implementation details and small environment changes~(\citealt{drl_matter}, \citealt{drl_matter_bis}). 
	Overcoming this sensitivity is key to making DRL applicable to real world problems.
	In this paper, we study the sensitivity of Deep Reinforcement learning algorithms to
	time discretization. More precisely, we show that approaches based on estimations of the
	Q-function, e.g. \emph{Deep Q-learning}~\cite{dqn} and \emph{Deep deterministic policy gradient}~\cite{ddpg}
	are sensitive to variations of time discretization. We further show that a simple reparameterization of the
	Q-function as a sum of a state value term and a \emph{small} action dependent advantage term yields an algorithm
	much more resilient to variations of time discretization.
\end{abstract}

>>>>

% Recommended, but optional, packages for figures and better typesetting:
\usepackage{amsmath, amssymb, amsthm}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{booktabs} % for professional tables
\usepackage{array}
\usepackage{xcolor}
\usepackage{algorithmic}

@@

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}

@@

\begin{abstract}
	Despite remarkable successes, \emph{Deep Reinforcement learning} remains sensitive to
	hyperparameterization, implementation details and small environment changes~(\citealt{drl_matter}, \citealt{drl_matter_bis}). 
	Overcoming this sensitivity is key to making DRL applicable to real world problems.
	In this paper, we study the sensitivity of Deep Reinforcement learning algorithms to
	time discretization \LB{in near-continuous time environments}. More precisely, we show that approaches based on estimations of the
	Q-function, e.g. \emph{Deep Q-learning}~\cite{dqn} and \emph{Deep deterministic policy gradient}~\cite{ddpg}
	are sensitive to variations of time discretization. We further show that a simple reparameterization of the
	Q-function as a sum of a state value term and a \emph{small} action dependent advantage term yields an algorithm
	much more resilient to variations of time discretization.\LB{Change last sentence to: We introduce a more resilient algorithm to variations of time discretization [We could say more, but still less that what is already there]}
\end{abstract}

### 2019-01-14 paper/icml_drau/intro.tex

\section{Introduction}
\label{sec:intro}
In recent years, deep learning based approaches to reinforcement learning have
thrived and provided impressive results in a variety of domains, achieving superhuman
performances with no expert knowledge in perfect information zero-sum
games~\cite{alphazero}, reaching level of top players in video
games~(\citealt{openai_five}, \citealt{dqn}), or learning dexterous manipulation
from scratch without demonstrations~\cite{hand_control}.

@@

In this paper we focus our attention on the sensitivity to time discretization
of DRL approaches, i.e. what happens when an agent receives $50$ observations
and is expected to take $50$ actions per second instead of $10$. One expects
that decreasing time discretization, or equivalently shortening reaction time,
should only improve agent performances. This is not what happens in practice
for approaches based on estimation of state action value functions, e.g.
\emph{Deep Q-learning} (DQN~\citep{dqn} and \emph{Deep deterministic policy
gradient} (DDPG~\citep{ddpg}). This is shown experimentally in Sec.~\ref{sec:exp}.

We relate this sensitivity to the fact that, as the discretization timestep
decreases, the effect of individual actions on the total return decreases, and
can vanish when the discretization timestep becomes infinitesimal. The natural
framework to study this phenomenon is Continuous time reinforcement learning 
(Sec.~\ref{sec:continous}).

To cope for this effect, we introduce a
parameterization of the Q-function as a sum of a state value term and a
\emph{small} action dependent advantage term (Sec.~\ref{subsec:reparam}). This
reparameterized Q approximation can be trained with deep variants of Q-learning
(Sec.~\ref{subsec:algorithm}).  To properly scale w.r.t. time discretization,
particular attention has to be taken regarding both the exploration method, and
the scaling of learning rates (Sec.~\ref{subsec:lr}, Sec.~\ref{subsec:explo}).
The resulting algorithm is shown to provide near perfect invariance to time
discretization on simple environments, and much better invariance properties
than vanilla DQN or DDPG on more complex environments (Sec.~\ref{sec:exp}).

>>>>

%! TEX root = icml_drau.tex

\section{Introduction}
\label{sec:intro}
In recent years, deep learning based approaches to reinforcement learning have
thrived and provided impressive results in a variety of domains, achieving superhuman
performances with no expert knowledge in perfect information zero-sum
games~\cite{alphazero}, reaching level of top players in video
games~(\citealt{openai_five}, \citealt{dqn}), or learning dexterous manipulation
from scratch without demonstrations~\cite{hand_control}. \LB{I would merge these two paragraphs.}

@@

In this paper we focus our attention on the sensitivity to time discretization
of DRL approaches \LB{in \emph{near-continuous} environments (control, ...},
i.e. what happens when an agent receives $50$ observations
and is expected to take $50$ actions per second instead of $10$. One expects
that decreasing time discretization, or equivalently shortening reaction time,
should only improve agent performances. This is not what happens in practice
for approaches based on estimation of state action value functions, e.g.
\emph{Deep Q-learning} (DQN~\citep{dqn} and \emph{Deep deterministic policy
gradient} (DDPG~\citep{ddpg}). This is shown experimentally in Sec.~\ref{sec:exp}.

We relate this sensitivity to the fact that, as the discretization timestep
decreases, the effect of individual actions on the total return decreases, and
can vanish when the discretization timestep becomes infinitesimal. The natural
framework to study this phenomenon is Continuous time reinforcement learning 
(Sec.~\ref{sec:framework}).

To cope for this effect, we introduce a
parameterization of the Q-function as a sum of a state value term and a
\emph{small} action dependent advantage term (Sec.~\ref{subsec:reparam}). This
reparameterized Q approximation can be trained with deep variants of Q-learning
(Sec.~\ref{subsec:algorithm}).  To properly scale w.r.t. time discretization,
particular attention has to be taken regarding both the exploration method, and
the scaling of learning rates (Sec.~\ref{subsec:lr}, Sec.~\ref{subsec:explo}).
The resulting algorithm is shown to provide near perfect invariance to time
discretization on simple environments, and much better invariance properties
than vanilla DQN or DDPG on more complex environments (Sec.~\ref{sec:exp}).
\LB{I think I would give less details, especially at the beginning, but insist on the methodology
  (all quantities and algorithms should have meaningful limits when $\deltat \rightarrow 0$)}

\LB{We should say somewhere that more invariance should mean less time spent to find hyperparameters}

\LB{Our main contributions are:
  \begin{itemize}
  \item We show that the Q-function is ill-defined in continuous environments, and thus that
    RL methods based on the Q-function (Q-learning, DDPG) are not robust to variations of time discretization.
  \item We introduce an algorithm (NAME?) resilient to time discretization \TODO{say more}
  \end{itemize}
}
